### 2013-07-11 mcmc.tex
troubleshooting text

>>>>

\section{Troubleshooting}

\paragraph{functional testing:}
...Run on standard distributons.

...Set likelihood to 1 and check that you sample your prior pdf.

\paragraph{low acceptance fraction:}
If you find that you are getting low acceptance fraction
  (in standard M-H MCMC or other varieties for which there is such a concept)
  you can simply reduce the sizes of the steps you consider to increase the fraction that are accepted.
This means decreasing the variance of the proposal distribution,
  or whatever parameter or parameters control the width of that distribution.
If reducing the variance of the proposal distribution does \emph{not} increase the acceptance fraction,
  then \emph{you have a bug}.
You must find that bug by auditing your code or else returning to the functional tests listed above.

Similarly for high acceptance fraction:
If you are finding a high acceptance fraction,
  then increasing the variance of the proposal distributon \emph{must} decrease the acceptance fraction.
If it does \emph{not}, then \emph{you have a bug}.

\paragraph{sticky chains:}
...Appearance of good and bad chains (show examples).

\paragraph{initialization-dependence:}
...Different initializations leading to different posterior samplings?

...Jammed ensemble sampler?

\paragraph{parameterization problems:}
...Degeneracies and duplications in parameter space; reparameterizations.
